---
title: "Analysis for Final Project TAKE 2"
description: |
  Preliminary Analysis on Text
author:
  - name: Lissie Bates-Haus, Ph.D. 
    url: https://github.com/lbateshaus
    affiliation: U Mass Amherst DACSS MS Student
    affiliation_url: https://www.umass.edu/sbs/data-analytics-and-computational-social-science-program/ms
date: "`r Sys.Date()`"
output: distill::distill_article
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

When I go back to my original research question, it is this:

How are ethical standards related to experimental research dissemenated to students, young professionals and to an academic discipline as a whole? I have uploaded the PowerPoint I created for the DACSS Three Minute Thesis research presentation [on my github](https://github.com/lbateshaus/Ethics/blob/main/Three%20Minute%20Thesis%20Presentation.pptx).

From my pilot study:

The general topics that were searched on included:

+ Was there any mention of ethics in the article?

+ Was IRB approval reported?

+ Was informed consent obtained by the researchers from the research participants?

+ Was potential harm to research subjects or staff discussed?

Searches included:

+ "ethic-"

+ "IRB", "institutional", "review board", "human", "subjects", "committee"

+ "informed", "consent"

+"harm", "burden", "mitigat-", "minimi-" and "safe-"

+ "informed", "consent"

+ "benefit"

In addition, assessment was made as to the following:

+ Was contact information for the authors provided?

+ How were research subjects selected and/or recruited?

+ Was the study registered or preregistered?

+ Was the general conflict of interest disclosure included in the article?

+ Was the data made publicly available?

+ Was any financial support or funding acknowledged?

What information am I looking for?

1.  Number of documents (aka journal articles) that contain the word ethics, by Journal
  +   Steps for the process:
  +   Tokenize my documents?
  +   Run count?

2. Do I want to include all of the search terms I used in my pilot study? 

3. Can I connect my authors with ethics mentions? And connect to my Networks project?

```{r warning=FALSE}
library(quanteda)
library(readr)
library(dplyr)
```

Trying something based on code found [here](https://slcladal.github.io/convertpdf2txt.html). 

### Reading in the Texts

_American Journal of Political Science_

```{r}
#function to perform pdf to text conversion for many documents
#Just for AJPS for now

convertpdf2txt <- function(dirpath){
  files <- list.files(dirpath, full.names = T)
  x <- sapply(files, function(x){
  x <- pdftools::pdf_text(x) %>%
  paste(sep = " ") %>%
  stringr::str_replace_all(fixed("\n"), " ") %>%
  stringr::str_replace_all(fixed("\r"), " ") %>%
  stringr::str_replace_all(fixed("\t"), " ") %>%
  stringr::str_replace_all(fixed("\""), " ") %>%
  paste(sep = " ", collapse = " ") %>%
  stringr::str_squish() %>%
  stringr::str_replace_all("- ", "") 
  return(x)
    })
}

```

Now apply the function to the directory:

```{r}
AJPStxts <- convertpdf2txt("~/DACSS/697D Text as Data/Final Project Materials/Articles pdfs/American Journal of Political Science")

# inspect the structure of the txts element
#str(AJPStxts)

#Create Corpus
AJPScorpus <- corpus(AJPStxts)
AJPSsummary <- summary(AJPScorpus)
AJPSsummary                       
```

OKAY THIS LOOKS MORE PROMISING!!  

Now to repeat for the other journals.

_American Political Science Review_

```{r}
APSRtxts <- convertpdf2txt("~/DACSS/697D Text as Data/Final Project Materials/Articles pdfs/American Political Science Review")

# inspect the structure of the txts element
#str(APSRtxts)

#Create Corpus
APSRcorpus <- corpus(APSRtxts)
APSRsummary <- summary(APSRcorpus)
APSRsummary                       
```

_American Politics Research_

```{r}
APRtxts <- convertpdf2txt("~/DACSS/697D Text as Data/Final Project Materials/Articles pdfs/American Politics Research")

# inspect the structure of the txts element
#str(APRtxts)

#Create Corpus
APRcorpus <- corpus(APRtxts)
APRsummary <- summary(APRcorpus)
APRsummary                       
```

_Journal of Experimental Political Research_

```{r}
JEPStxts <- convertpdf2txt("~/DACSS/697D Text as Data/Final Project Materials/Articles pdfs/Journal of Experimental Political Science")

# inspect the structure of the txts element
#str(JEPStxts)

#Create Corpus
JEPScorpus <- corpus(JEPStxts)
JEPSsummary <- summary(JEPScorpus)
JEPSsummary                       
```

_Political Science Research and Methods_

```{r}
PSRMtxts <- convertpdf2txt("~/DACSS/697D Text as Data/Final Project Materials/Articles pdfs/Political Science Research and Methods")

# inspect the structure of the txts element
#str(PSRMtxts)

#Create Corpus
PSRMcorpus <- corpus(PSRMtxts)
PSRMsummary <- summary(PSRMcorpus)
PSRMsummary                       
```

_Research and Politics_

```{r}
RAPtxts <- convertpdf2txt("~/DACSS/697D Text as Data/Final Project Materials/Articles pdfs/Research and Politics")

# inspect the structure of the txts element
#str(RAPtxts)

#Create Corpus
RAPcorpus <- corpus(RAPtxts)
RAPsummary <- summary(RAPcorpus)
RAPsummary                       
```

### Some Exploration

```{r}

AJPSdata_tokens <- tokens(AJPScorpus)
kwic(AJPSdata_tokens, pattern = "ethics")

```

This is something to explore. In my original pilot study, I had 28 articles from the AJPS and had a count of 13 articles mentioning the word ethi* - so perhaps it's a stemming issue?

```{r}
kwic(AJPSdata_tokens, pattern = phrase("IRB approval"))
```



